DNSKEY Management

### 2012-12-03 paper/paper.tex
Nicely typeset abstract

\usepackage{graphicx}
%\usepackage{hyperref}
\usepackage{url}

@@

\maketitle

>>>>

\usepackage{graphicx}
%\usepackage{hyperref}
\usepackage{url}
\usepackage{abstract}

@@

\twocolumn[
\maketitle
\begin{onecolabstract}
  In this paper we recapitutale the current deployment status of
  DNSSEC and go into the main issues when managing its keys. It
  outlines the paper ``Interadministrative Challenges in Managing
  DNSKEYs'' \cite{Osterweil09} and updates some of its contents
  especially with respect to the signing of the root zone on July
  15, 2012. We will see that DNSSEC penetration in the Internet's
  zones is still low but that the necessary foundations have been lain
  for full deployment.
\end{onecolabstract}
\vspace{\baselineskip}
]
